Advantages of mixed unitary operators for quantum information processing

### 2019-01-07 decorrelation/mixed_unitaries.tex
a few more small changes
extra ^T
cleaning up equations
Trying to extend the mixing lemma

\documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
 \usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{calc}
\graphicspath{{./figures/}}
\hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=Decorrelating Errors}
\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\ident}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}
\newcommand{\erf}[1]{Eq.~(\ref{#1})}
\newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
\newcommand{\note}[1]{{\color{red}[#1]}}
\newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}
\newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}

\newcommand{\actual}{\ensuremath{\tilde{\mathcal{G}}}}
\newcommand{\target}{\ensuremath{{\mathcal{G}}}}
\newcommand{\error}{\ensuremath{{\mathcal{E}}}}

@@

% ==============================================================================
% Section: Mathematical preliminaries
% ==============================================================================
\section{Mathematical preliminaries}
\label{sec:representing_quantum_gates}
Quantum gate operations are implemented by applying a sequence of classical control fields to some set of qubits. Fluctuations in the environment or imperfections in the controls can cause the state of the qubits to change in a way that is different from what was intended.  But if the gates are fairly stable with time and context\cite{1810.05651}, then we can usually describe their action on the qubit state using \emph{process matrices} -- linear, Markovian maps on the state of some qubits.  When working with process matrices, it is convenient to write the system density operator using a vectorized representation, and in this article, we'll make use of the generalized Bloch vector,
\begin{equation}
  \vec \rho = \tr(\rho \vec \Sigma),
\end{equation}
where $\vec \Sigma$ is a vector of all $4^n$ $n$-qubit Pauli operators. The action of a gate is then given by the usual matrix multiplication:
\begin{equation}\label{error_def}
  \vec\rho \rightarrow \target\vec\rho = \error \actual \vec\rho.
\end{equation}
Here $\target$ is the target operation, $\actual$ is the actual gate as implemented, and $\error$ is the effective error channel:

\begin{equation}\label{eq:process_matrix}
\error =
	\left(\begin{array}{c|cccc}
		1 &  & \vec{0}^T & \\ 
		\hline & &  &  \\
		\vec{m} &  & R &  \\
		 &  &  & 
	\end{array} 	
	\right)
\end{equation}
The top row of all trace-preserving (TP) maps is fixed to $\{1,0,0,0,\cdots\}$.  The rest of the first column, $\vec{m}$, describes any deviations from unitality, as could arise from amplitude damping. If the error channel is unitary, then the error is coherent, and the submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector. If  $R$ is diagonal, then the error channel is Pauli stochastic, with each entry  corresponding to the probability that the associated Pauli error occurs in each application of the gate. That is to say that $\error_{ii}$ gives the probability that the following map is applied:
\begin{equation}
\vec\rho \rightarrow \tr{(\sigma_j^{\dagger}\sigma_i\sigma_k\sigma_i^{\dagger})}\vec{\rho}
\end{equation}
 If R is symmetric but not diagonal, then the channel is still stochastic, but the random errors consist of correlated Pauli operators (such as $X+Y$). For a single qubit, this describes everything, but the situation can be slightly more complicated for more qubits.

For a collection of single qubit controls $\{U_i\}$ generated by $\{H_i\}$, the channel that results in general has elements:
\begin{align}
	\mathcal{M}_{jk} 
		=& \sum_i p_i \tr{(\sigma_j^{\dagger}U\sigma_kU^{\dagger})} \\
		=& \sum_i p_i \tr{(\sigma_j^{\dagger} \exp(i \frac{\theta_i}{2} H_i)\sigma_k		\exp(-i \frac{\theta_i}{2} H_i)}) \\
		=& \tr{\sum_i p_i (\sigma_j^{\dagger} (\cos\theta_i + i \sin\theta_i H_i) \sigma_k		(\cos\theta_i - i \sin\theta_i H_i))} \\
		=& \tr (\sum_i p_i (\sigma_j\sigma_k\cos\theta_i^2 + \sigma_jH_i\sigma_k H_i\sin\theta_i^2 \\ 
		&+ iH_i\sigma_k\sin\theta_i\cos\theta_i - i\sigma_j H_i\sin\theta_i\cos\theta_i))
\end{align}
The first term corresponds to the identity, and $\sin\theta^2$ is always positive, so we cannot hope to eliminate the second term, but $\sin\theta\cos\theta$ may be positive or negative, and so there is hope that we could possibly combine various implementations to eliminate this term. The result would be a purely stochastic channel.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{vectorspace.pdf}
  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error. These error Hamiltonians lie in a vector space. a) Four effective Hamiltonians. The origin is not contained in their convex hull, so there are no balanced control solutions. b) The origin is contained in the covex hull after adding an additional control solution. Because there are more than $n+1$ implementations, there exist an infinite number of balanced control solutions. c) The error Hamiltonians shown with their derivative with respect to a control parameter. As this parameter drifts, a $0^{\rm th}$-order balanced control solution may drift, leading to a first-order error. d) The derivatives also lie in a vector space. If the origin lies in their convex hull, then it may be possible to construct a $1^{\rm{st}}$-order mixed unitary process.}
  \label{fig:vectorspace}
\end{figure}

The problem of minimizing $\sin\theta\cos\theta$ can equivalently be cast as trying to construct a family of vectors, $\sin\theta\cos\theta(H_i\sigma_k - \sigma_jH_i)$ whose convex hull contains the origin. This can be seen in Figure \ref{fig:vectorspace} a) and b).

@@

A \textit{mixed unitary process} (MUP) consists of a set of unitary channels, $\actual_j$, and associated weights, $\sum_j \omega_j = 1$.  The process matrix for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_j \omega_j \actual_j$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_j \omega_j \error_j$. From this definition, we can compute the AGI of a MUP, by first computing the AGI of an convex combination of channels:
\begin{align}
\mathcal{F}(\alpha\error_1 + (1-\alpha)\error_2) &= \frac{\tr(\alpha\error_1 + (1-\alpha)\error_2) + d}{d^2 + d} \\
&= \alpha\frac{\tr(\error_1) + d}{d^2 + d} + (1-\alpha)\frac{\tr(\error_2) + d}{d^2 + d} 
\end{align}
where we have used the linearity of the trace.
%\begin{align}
%\mathcal{F}(\error_{\rm M}) &= \mathcal{F}(\sum_j \omega_j \error_j)\\
%&= \frac{\tr (\sum_j \omega_j \error_j) + d}{d^2 + d}\\
%&= \frac{\sum_j(\tr (\omega_j \error_j)) + d}{d^2 + d}\\
%&= \frac{\sum_j(\tr (\omega_j (\error_j + d))}{d^2 + d}\\
%&= \sum_j\frac{(\tr (\omega_j (\error_j + d))}{d^2 + d}\\ 
%\end{align}

@@

Campbell\cite{Campbell2017} considered this important problem of minimizing the diamond norm of the resulting error channel. Given a collection of component channels with error at most $\epsilon$, they show that if the Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed. The diamond norm is a particularly appealing target because the it provides useful error metrics on quantum circuits. However, it is not the only optimization target that can be chosen. If the ultimate goal is to produce a channel whose effect can be Monte Carlo simulated, then it may be useful instead to construct a channel whose errors are Pauli stochastic. Using a constrained numerical optimization routine, such a channel could be produced by minimizing the off-diagonal elements of $R$ in Equation \ref{eq:process_matrix}. Indeed, this is the approach we consider in Section \ref{sec:experimental_results}. More generally, the are a number of options one may wish to consider when selecting weights to prepare a mixed unitary process.

% ==============================================================================
% Section: Constructing Useful Unitary Processes
% ==============================================================================
\section{Constructing Useful Unitary Processes}
\label{sec:mixed_unitary_processes}
\subsection{Mixed Unitary Processes with Small Diamond Norm}
\label{sec:small_diamond_norm}
There are often many possibly ways of implementing any given target quantum gate. Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011} By selecting from these various implementations at random, they show that the resulting quantum channel can be made to have significantly reduced coherent error.  As a simple example of how this occurs, consider a scenario in which we have a single-qubit and four possible implementations of a $\pi$-pulse about the $\sigma_x$ axis. The error channels for these four implementations are themselves unitary rotations about the $\sigma_x$ axis with rotation angles of $\{-2\epsilon, -\epsilon, \epsilon, 2\epsilon\}$. Such a situation could appear, for instance, if there were amplitude errors on the fields used to affect the gates, and if the control could be implemented by a rotation about the positive or negative $\sigma_x$ axis.

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{simple_example.pdf}
  \caption{An example of a mixed unitary process. Using optimal control, two implementations of a $Z_\pi$ gate are designed to have equal and opposite sensitivity to errors (if one implementation over-rotates by angle $\theta$, then the other \emph{under}-rotates by $\theta$). Each time the gate is used, one of these implementations is chosen at random. The resulting quantum channel is equivalent to a perfect implementation of the gate followed by dephasing of $\order{\theta^2}$.}
  \label{fig:simple_example}
\end{figure}

@@

While mixed unitary processes offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance. Because of this drift, the quality of the MUP will degrade. Thus, we would like to design MUPs that are \textit{robust} to this drift. To enforce robustness, we can consider higher derivatives of the Hamiltonians in \ref{eq:campbell-condition}. Instead of just requiring that the $0^{th}$ derivative averages to zero, we should impose a similar condition on the derivatives of the Hamiltonians with respect to parameters that may drift:
\begin{equation}
D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}H_j(\vec{\delta})|_{\delta=\vec{0}}
\end{equation}
Then we say that a mixed unitary process is said to be robust to order $\ell$ (an $\ell$MUP) if for all $1 \leq j \leq \ell$:
\begin{equation}\label{eq:MUP}
\begin{gathered}
\sum_j\omega_j(\sum_{n=0}^k D^n_j)^k = 0\\
\end{gathered}
\end{equation}
In particular, we see that a 0MUP satisfies Equation \ref{eq:campbell-condition}. More generally, these conditions imply that an $\ell$MUP is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$. To see this, we can rewrite the error on each control in the MUP as:
\begin{equation}\label{eq:taylor}
\begin{gathered}
\actual_j(\vec{\delta}) = \exp(-i(H_j(\vec{0}) + \frac{\partial}{\partial\delta_i}H_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} H_j(d\delta_i d\delta_k) + \ldots))\target
\end{gathered}
\end{equation}
By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one finds that the the first $\ell$ derivatives of an $\ell MUP$ will be zero. Furthermore, if we are only interested in being first order insensitve to drift and can select controls such that $|D_j^n|\approx\epsilon$, we see that Equation \ref{eq:MUP} can be approximated as:
\begin{equation}\label{eq:MUP-relaxed}
\begin{gathered}
\sum_k\omega_jD^n_j = 0\\
\end{gathered}
\end{equation}
This condition guarantees that errors will be supressed quadratically for all derivatives up to order $\ell$. Following from Lemma 2 in \cite{Campbell2017}, if $0\in $ Conv$[\{H_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then we know that an $\vec{\omega}$ exists that quadratically decreases the diamond norm. This condition is illustrated in Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell MUP$.

To generate robustly mixed unitary processes, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to \ref{eq:vectorized_hamiltonians}:
\begin{equation}
{D^{\ell}}^T =  \left(\begin{array}{cccc}
		D^\ell_{1_{11}} & D^\ell_{2_{21}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		D^\ell_{m_{11}} &  &  D^\ell_{m_{nn}} \\ 
	\end{array} 	
	\right)
\end{equation}

@@

%\begin{equation}\label{eq:minimization_l2}
%  \begin{split}
%    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||_2 + \eta\sum||D_0^T\omega||_2\\
%  \end{split}
%\end{equation}
\subsection{Sparsity Constraints}
As a practical consideration, we would also like to regularize our objective function to enforce sparsity. Control electronics often have a limited amount of waveform memory, and thus it is important that MUPs have non-trivial probability support on a small number of controls. As an example of where this would be necessary is Figure\ref{fig:vectorspace}. In Subfigure b, it's clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators. However, if we additionally want our controls to form a 1MUP, we see from Subfigure D that we need $H_4$ in our control set. Thus we would like the solver to be frugal in which controls it selects. In many machine learning situation, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity, however here it is insufficient as we already constrain the one norm of the vector we optimize over to be one. Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:

@@

@@

In this example it was infeasible to use GRAPE to return non-trivial solutions. Instead we manually selected piecewise constant echoing sequences with 500 steps and total evolution time of $\frac{5\pi}{2}$. In particular, we considered $RX(\pi)$, $RX(-\pi)$, $RY(\pi)$ and $RY(-\pi)$ bang-bang sequences \cite{bangbang}, consisting of all combinations of simultaneous $\pi$ pulses activated at multiples of $8$ steps from the beginning of the controls, and the same multiple of $8$ steps prior to the end of the controls. An example of such a control is given in Figure \ref{fig:bangbang}. To give the control family a variety of RF errors, we added on uniformly distributed errors to each $\pi$ pulse, between $-.25$\% and $.25$\%.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{bangbang.png}
  \caption{Example bang-bang sequence, using both qubits' $\sigma_x$ controls. Not shown are the unused $\sigma_y$ controls, and the uncontrolled resonant exchange interaction.}
  \label{fig:bangbang}
\end{figure}

@@

% ==============================================================================
% Section: Experimental Results
% ==============================================================================

>>>>

\documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
 \usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{calc}
\graphicspath{{./figures/}}
\hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=Decorrelating Errors}
\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\ident}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}
\newcommand{\erf}[1]{Eq.~(\ref{#1})}
\newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
\newcommand{\note}[1]{{\color{red}[#1]}}
\newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}
\newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}
\newcommand{\deriv}[0]{{\frac{d}{d\vec{\delta}}}}
\newcommand{\actual}{\ensuremath{\tilde{\mathcal{G}}}}
\newcommand{\target}{\ensuremath{{\mathcal{G}}}}
\newcommand{\error}{\ensuremath{{\mathcal{E}}}}
\def\id{\mbox{\small 1} \!\! \mbox{1}}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth]{simple_example.pdf}
  \caption{An example of a mixed unitary process. Using optimal control, two implementations of a $Z_\pi$ gate are designed to have equal and opposite sensitivity to errors (if one implementation over-rotates by angle $\theta$, then the other \emph{under}-rotates by $\theta$). Each time the gate is used, one of these implementations is chosen at random. The resulting quantum channel is equivalent to a perfect implementation of the gate followed by dephasing of $\order{\theta^2}$.}
  \label{fig:simple_example}
\end{figure}
% ==============================================================================
% Section: Mathematical preliminaries
% ==============================================================================
\section{Mathematical preliminaries}
\label{sec:representing_quantum_gates}
Quantum gate operations are implemented by applying a sequence of classical control fields to some set of qubits. Fluctuations in the environment or imperfections in the controls can cause the state of the qubits to change in a way that is different from what was intended.  But if the gates are fairly stable with time and context\cite{1810.05651}, then we can usually describe their action on the qubit state using \emph{process matrices} -- linear, Markovian maps on the state of some qubits.  When working with process matrices, it is convenient to write the system density operator using a vectorized representation, and in this article, we'll make use of the generalized Bloch vector,
\begin{equation}
  \vec \rho = \tr(\rho \vec \Sigma),
\end{equation}
where $\vec \Sigma$ is a vector of all $4^n$ $n$-qubit Pauli operators. The action of a gate is then given by the usual matrix multiplication:
\begin{equation}\label{error_def}
  \vec\rho \rightarrow \target\vec\rho = \error \actual \vec\rho.
\end{equation}
Here $\target$ is the target operation, $\actual$ is the actual gate as implemented, and $\error$ is the effective error channel:

\begin{equation}\label{eq:process_matrix}
\error =
	\left(\begin{array}{c|cccc}
		1 &  & \vec{0}^T & \\ 
		\hline & &  &  \\
		\vec{m} &  & R &  \\
		 &  &  & 
	\end{array} 	
	\right)
\end{equation}
The top row of all trace-preserving (TP) maps is fixed to $\{1,0,0,0,\cdots\}$.  The rest of the first column, $\vec{m}$, describes any deviations from unitality, as could arise from amplitude damping. If the error channel is unitary, then the error is coherent, and the submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector. If  $R$ is diagonal, then the error channel is Pauli stochastic, with each entry  corresponding to the probability that the associated Pauli error occurs in each application of the gate. That is, $\error_{ii}$ gives the probability that the following map is applied:
\begin{equation}
\vec\rho_k\rightarrow\sum_j\tr{(\sigma_j^{\dagger}\sigma_i\sigma_k\sigma_i^{\dagger})}\vec{\rho_k}
\end{equation}
 If R is symmetric but not diagonal, then the channel is still stochastic, but the random errors consist of correlated Pauli operators (such as $X+Y$). For a single qubit, this describes everything, but the situation can be slightly more complicated for more qubits.

For a collection of single qubit controls $\{U_i\}$ generated by $\{H_i\}$, the channel that results in general has elements:
\begin{align}
	\mathcal{M}_{jk} 
		=& \sum_i p_i \tr{(\sigma_j^{\dagger}U\sigma_kU^{\dagger})} \\
		=& \sum_i p_i \tr{(\sigma_j^{\dagger} \exp(i \frac{\theta_i}{2} H_i)\sigma_k		\exp(-i \frac{\theta_i}{2} H_i)}) \\
		=& \tr (\sum_i p_i (\sigma_j^{\dagger}\sigma_k\cos\theta_i^2 + \sigma_j^{\dagger}H_i\sigma_k H_i\sin\theta_i^2 \\ 
		&+ i\sigma_j^{\dagger}H_i\sigma_k\sin\theta_i\cos\theta_i - i\sigma_j^{\dagger}\sigma_kH_i\sin\theta_i\cos\theta_i))
\end{align}
The first term corresponds to the identity, and $\sin\theta^2$ is always positive, so we cannot hope to eliminate the second term, but $\sin\theta\cos\theta$ may be positive or negative, and so there is hope that we could possibly combine various implementations to eliminate this term. The result would be a purely stochastic channel.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{vectorspace.pdf}
  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error. These error Hamiltonians lie in a vector space. a) Four effective Hamiltonians. The origin is not contained in their convex hull, so there are no 0MUPs. b) The origin is contained in the covex hull after adding an additional control solution. Because there are more than $n+1$ implementations, there exist an infinite number of 0MUPs. c) The error Hamiltonians shown with their derivative with respect to a control parameter. As this parameter drifts, a 0MUP may drift, leading to a first-order error. d) The derivatives also lie in a vector space. If the origin lies in their convex hull, then it may be possible to construct a 1MUP.}
  \label{fig:vectorspace}
\end{figure}

The problem of minimizing $\sin\theta\cos\theta$ can equivalently be cast as trying to construct a family of vectors, $\sin\theta\cos\theta(\sigma_j^{\dagger}H_i\sigma_k - \sigma_j^{\dagger}\sigma_kH_i)$ whose convex hull contains the origin. This can be seen in Figure \ref{fig:vectorspace} a) and b).

@@

A \textit{mixed unitary process} (MUP) consists of a set of unitary channels, $\actual_j$, and associated weights, $\sum_j \omega_j = 1$.  The process matrix for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_j \omega_j \actual_j$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_j \omega_j \error_j$. From this definition, we can compute the AGI of a MUP, by first computing the AGI of an convex combination of channels:
\begin{align}
\mathcal{F}(\alpha\error_1 + (1-\alpha)\error_2) = \frac{\tr(\alpha\error_1 + (1-\alpha)\error_2) + d}{d^2 + d} \\
= \alpha\frac{\tr(\error_1) + d}{d^2 + d} + (1-\alpha)\frac{\tr(\error_2) + d}{d^2 + d} \\
= \alpha\mathcal{F}(\error_1) + (1-\alpha)\mathcal{F}(\error_2)
\end{align}
where we have used the linearity of the trace.
%\begin{align}
%\mathcal{F}(\error_{\rm M}) &= \mathcal{F}(\sum_j \omega_j \error_j)\\
%&= \frac{\tr (\sum_j \omega_j \error_j) + d}{d^2 + d}\\
%&= \frac{\sum_j(\tr (\omega_j \error_j)) + d}{d^2 + d}\\
%&= \frac{\sum_j(\tr (\omega_j (\error_j + d))}{d^2 + d}\\
%&= \sum_j\frac{(\tr (\omega_j (\error_j + d))}{d^2 + d}\\ 
%\end{align}

@@

Campbell\cite{Campbell2017} considered the important problem of minimizing the diamond norm of the resulting error channel. Given a collection of component channels with error at most $\epsilon$, he showed that if the Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed. The diamond norm is a particularly appealing target because the it provides useful error metrics on quantum circuits. However, it is not the only optimization target that can be chosen. If the ultimate goal is to produce a channel whose effect can be Monte Carlo simulated, then it may be useful instead to construct a channel whose errors are Pauli stochastic. Using a constrained numerical optimization routine, such a channel could be produced by minimizing the off-diagonal elements of $R$ in Equation \ref{eq:process_matrix}. Indeed, this is the approach we consider in Section \ref{sec:experimental_results}. More generally, the are a number of options one may wish to consider when selecting weights to prepare a mixed unitary process.

% ==============================================================================
% Section: Constructing Useful Unitary Processes
% ==============================================================================
\section{Constructing Useful Unitary Processes}
\label{sec:mixed_unitary_processes}
\subsection{Diamond Norm Minimization}
\label{sec:small_diamond_norm}
There are often many possibly ways of implementing any given target quantum gate. Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011} By selecting from these various implementations at random, they show that the resulting quantum channel can be made to have significantly reduced coherent error.  As a simple example of how this occurs, consider a scenario in which we have a single-qubit and four possible implementations of a $\pi$-pulse about the $\sigma_x$ axis. The error channels for these four implementations are themselves unitary rotations about the $\sigma_x$ axis with rotation angles of $\{-2\epsilon, -\epsilon, \epsilon, 2\epsilon\}$. Such a situation could appear, for instance, if there were amplitude errors on the fields used to affect the gates, and if the control could be implemented by a rotation about the positive or negative $\sigma_x$ axis.

@@

@@

While mixed unitary processes offer significant improvements to gate performance, they fail to take into account the reality that most control electronics experience drift over time scales relevant to QIP performance. Because of this drift, the quality of the MUP will degrade. Thus, we would like to design MUPs that are \textit{robust} to this drift. To enforce robustness, we can consider higher derivatives of the Hamiltonians in \ref{eq:campbell-condition}. Instead of just requiring that the $0^{th}$ derivative averages to zero, we should impose a similar condition on the derivatives of the Hamiltonians with respect to parameters that may drift:
\begin{equation}
D^n_j = \frac{1}{n!}\frac{\partial^{n}}{\partial\delta_{i_1}\ldots\partial\delta_{i_n}}H_j(\vec{\delta})|_{\delta=\vec{0}}
\end{equation}
Then we say that a mixed unitary process is said to be robust to order $\ell$ (an $\ell$MUP) if for all $1 \leq j \leq \ell$:
\begin{equation}\label{eq:MUP}
\begin{gathered}
\sum_j\omega_j(\sum_{n=0}^k D^n_j)^k = 0\\
\end{gathered}
\end{equation}
In particular, we see that a 0MUP satisfies Equation \ref{eq:campbell-condition}. More generally, these conditions imply that an $\ell$MUP is insensitive to the $\ell^{th}$ order in drift in $\vec{\delta}$. To see this, we can rewrite the error on each control in the MUP as:
\begin{equation}\label{eq:taylor}
\begin{gathered}
\actual_j(\vec{\delta}) = \exp(-i(H_j(\vec{0}) + \frac{\partial}{\partial\delta_i}H_j(d\delta_i)\\ +  \frac{1}{2}\frac{\partial^2}{\partial\delta_i\partial\delta_k} H_j(d\delta_i d\delta_k) + \ldots))\target
\end{gathered}
\end{equation}
By Taylor expanding Equation \ref{eq:taylor} in $\vec{\delta}$, one finds that the the first $\ell$ derivatives of an $\ell$MUP will be zero. Furthermore, if we are only interested in being first order insensitve to drift and can select controls such that $|D_j^n|\approx\epsilon$, we see that Equation \ref{eq:MUP} can be approximated as:
\begin{equation}\label{eq:MUP-relaxed}
\begin{gathered}
\sum_k\omega_jD^n_j = 0\\
\end{gathered}
\end{equation}
This condition guarantees that errors will be supressed quadratically for all derivatives up to order $\ell$. A proof is included in the appendix that generalizes the Hastings-Campbell Mixing Lemma in \cite{Campbell2017}. Namely, Campbell shows that if $0\in $ Conv$[\{H_i(\vec{\delta})\}]$, where Conv is the convex hull of its arguments, then an $\vec{\omega}$ exists that quadratically decreases the diamond norm. We prove that $0\in $ Conv$[\{D_j^n(\vec{\delta})\}]$ implies there is an $\vec{\omega}$ exists that quadratically decreases the $\ell^{th}$-order sensitivity of the diamond norm of an $\ell$MUP. This condition is illustrated in Figure \ref{fig:vectorspace} gives geometric intuition for the conditions required to produce an $\ell$MUP.

To generate robustly mixed unitary processes, we first define the vectorized derivative matrix ${D^{\ell}}$ in a similar way to \ref{eq:vectorized_hamiltonians}:
\begin{equation}
{D^{\ell}} =  \left(\begin{array}{cccc}
		D^\ell_{1_{11}} & D^\ell_{2_{21}} & \ldots   \\ 
		\vdots\ & \ddots &    \\
		D^\ell_{m_{11}} &  &  D^\ell_{m_{nn}} \\ 
	\end{array} 	
	\right)
\end{equation}

@@

%\begin{equation}\label{eq:minimization_l2}
%  \begin{split}
%    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||D_{\ell}^T\omega||_2 + \eta\sum||D_0^T\omega||_2\\
%  \end{split}
%\end{equation}
\subsection{Sparsity Constraints}
As a practical consideration, we would also like to regularize our objective function to enforce sparsity. Control electronics often have a limited amount of waveform memory, and thus it is important that MUPs have non-trivial probability support on a small number of controls. As an example of where this would be necessary is Figure \ref{fig:vectorspace}. In Subfigure b, it's clear that $H_4$ is unecessary to contain the origin in the convex hull of the error generators. However, if we additionally want our controls to form a 1MUP, we see from Subfigure D that we need $H_4$ in our control set. Thus we would like the solver to be frugal in which controls it selects. In many machine learning situation, lasso regularization \cite{tibshirani1996regression} can be used to enforce sparsity, however here it is insufficient as we already constrain the one norm of the vector we optimize over to be one. Conveniently, the problem of enforcing sparsity in such situations has been considered in \cite{NIPS2012_4504} and can be expressed via another convex program that extends Equation \ref{eq:minimization}:

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{SQRTY_no_member.png}
  \caption{Numerical results comparing a 0MUP to a 1MUP for a single tunable qubit, for $RY(\frac{\pi}{2})$. The results are qualitatively similar to those for $RX(\frac{\pi}{2})$. In this case the 0MUP outperforms both the 1MUP by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin. However, varying over $\delta$ we see that the 1MUP outperforms the 0MUP by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.}
  \label{fig:YMUP}
\end{figure}

@@

In this example it was infeasible to use GRAPE to return non-trivial solutions. Instead we manually selected piecewise constant echoing sequences with 500 steps and total evolution time of $\frac{5\pi}{2}$. In particular, we considered $RX(\pi)$, $RX(-\pi)$, $RY(\pi)$ and $RY(-\pi)$ bang-bang sequences \cite{bangbang}, consisting of all combinations of simultaneous $\pi$ pulses activated at multiples of $8$ steps from the beginning of the controls, and the same multiple of $8$ steps prior to the end of the controls. To give the control family a variety of RF errors, we added on uniformly distributed errors to each $\pi$ pulse, between $-.25$\% and $.25$\%.

%\begin{figure}
%  \centering
%  \includegraphics[width=\columnwidth]{bangbang.png}
%  \caption{Example bang-bang sequence, using both qubits' $\sigma_x$ controls. Not shown are the unused $\sigma_y$ controls, and the uncontrolled resonant exchange interaction.}
%  \label{fig:bangbang}
%\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{2QRBC_no_member.png}
  \caption{Numerical results comparing a 0MUP to a 1MUP for a pair of tunable qubits, with a resonant exchange interaction. Shown with lower alpha values are example constituent controls. The 0MUP and 1MUP can be seen to outperform these controls by half of an order of magnitude at the origin. For all detuning values the 1MUP performs as well or better than the 0MUP. When there is $.2\%$ drift in the qubit frequency, the 1MUP outperforms members of the control famlies by almost an order of magnitude in diamond norm. Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MUP outperforms the the constituent controls by over half an order of magnitude.}
  \label{fig:2MUP}
\end{figure}
% ==============================================================================
% Section: Experimental Results
% ==============================================================================
